---
title: "Data Cleaning Controls"
author: "Sarah Wenzel"
date: "12 1 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r libraries}
library(tidyverse)
library(countrycode)
library(janitor)
library(readxl)
library(fastDummies)
options(scipen=999)

```

# Cleaning World Bank control variables

Those countries that only contained NAs were collected in a vector and removed when cleaning the data

```{r}

na_countries <- c("Channel Islands", "Kosovo", "British Virgin Islands", "French Polynesia", "Gibraltar", "Korea, Dem. People's Rep.", "Sint Maarten (Dutch part)", "St. Martin (French part)", "")

```

## Current USD GDP
Used to transform investments into a share of the receiving country's GDP

```{r gdp}

gdp <- read.csv(here::here("04_data_cleaning/controls/World Bank/WB_current_USD_GDP_Data.csv"))%>%
  janitor::clean_names()%>%  
  subset(select = -c(i_series_name, series_code, country_code))%>%
  rename(country = country_name)%>%
  pivot_longer(cols = !country, names_to = "year", values_to = "gdp")%>%
  mutate(year=substr(year,9,12))%>%
  mutate(iso = countrycode(country, origin = 'country.name', destination = 'iso3c'))%>%
  mutate(country = countrycode(country, origin = 'country.name', destination = 'country.name'))%>%
  filter(!country %in% na_countries)%>%
  mutate_at(c("year", "gdp"), as.numeric)

write.csv(gdp, here::here("05_clean_data/current_usd_gdp.csv"), row.names = FALSE)

```

## Per capita GDP (used as control in regression analysis)

```{r per capita gdp}
pc_gdp <- read.csv(here::here("04_data_cleaning/controls/World Bank/WB_per_capita_GDP_Data.csv"))%>%
  janitor::clean_names()%>%  
  subset(select = -c(i_series_name, series_code, country_code))%>%
  rename(country = country_name)%>%
  pivot_longer(cols = !country, names_to = "year", values_to = "gdp")%>%
  mutate(year=substr(year,9,12))%>%
  mutate(iso = countrycode(country, origin = 'country.name', destination = 'iso3c'))%>%
  mutate(country = countrycode(country, origin = 'country.name', destination = 'country.name'))%>%
  filter(!country %in% na_countries)%>%
  mutate_at(c("year", "gdp"), as.numeric)

# sum(is.na(gdp$gdp))

write.csv(pc_gdp, here::here("05_clean_data/per_capita_gdp.csv"), row.names = FALSE)
```


###  Trade openness

```{r}

t_o <- read.csv(here::here("04_data_cleaning/controls/World Bank/World Bank Trade Openness_Data.csv"))%>%
  janitor::clean_names()%>%  
  subset(select = -c(i_series_name, series_code, country_code))%>%
  rename(country = country_name)%>%
  pivot_longer(cols = !country, names_to = "year", values_to = "trade_share_gdp")%>%
  mutate(year=substr(year,9,12))%>%
  mutate(iso = countrycode(country, origin = 'country.name', destination = 'iso3c'))%>%
  mutate(country = countrycode(country, origin = 'country.name', destination = 'country.name'))%>%
  filter(!country %in% na_countries)%>%
  mutate_at(c("year", "trade_share_gdp"), as.numeric)

write.csv(t_o, here::here("05_clean_data/trade_openness.csv"), row.names = FALSE)


```
### Industry share in GDP

```{r industry share}

i_s <- read.csv(here::here("04_data_cleaning/controls/World Bank/World_Bank_Industry_Share_GDP_Data.csv"))%>%
  janitor::clean_names()%>%  
  subset(select = -c(i_series_name, series_code, country_code))%>%
  rename(country = country_name)%>%
  pivot_longer(cols = !country, names_to = "year", values_to = "industry_share")%>%
  mutate(year=substr(year,9,12))%>%
  mutate(iso = countrycode(country, origin = 'country.name', destination = 'iso3c'))%>%
  filter(!country %in% na_countries)%>%
  mutate_at(c("year", "industry_share"), as.numeric)

test <- subset(i_s, is.na(industry_share)) #since more countries never reported their industry share compared to their gdp, even more countries could be removed from this dataset

write.csv(i_s, here::here("05_clean_data/industry_share_gdp.csv"), row.names = FALSE)

```
### Urban Population

```{r urbanization}

urban <- read.csv(here::here("04_data_cleaning/controls/World Bank/World_Bank_Urban_Population.csv"))%>%
  janitor::clean_names()%>%  
  subset(select = -c(i_series_name, series_code, country_code))%>%
  rename(country = country_name)%>%
  pivot_longer(cols = !country, names_to = "year", values_to = "urban_pop_share")%>%
  mutate(year=substr(year,9,12))%>%
  mutate(iso = countrycode(country, origin = 'country.name', destination = 'iso3c'))%>%
  filter(!country %in% na_countries)%>%
  mutate_at(c("year", "urban_pop_share"), as.numeric)

test <- subset(urban, is.na(urban_pop_share))

write.csv(urban, here::here("05_clean_data/urban_pop_share.csv"), row.names = FALSE)
```

### Population size

```{r}

pop_size <- read.csv(here::here("04_data_cleaning/controls/World Bank/World_Bank_population_size.csv"))%>%
  janitor::clean_names()%>%  
  subset(select = -c(i_series_name, series_code, country_code))%>%
  rename(country = country_name)%>%
  mutate_at(vars(-country), as.numeric)%>%
  pivot_longer(cols = !country, names_to = "year", values_to = "pop_size")%>%
  mutate(year=substr(year,9,12))%>%
  mutate(iso = countrycode(country, origin = 'country.name', destination = 'iso3c'))%>%
  filter(!country %in% na_countries)%>%
  mutate(year = as.numeric(year))

test <- subset(pop_size, is.na(pop_size))

write.csv(pop_size, here::here("05_clean_data/population_size.csv"), row.names = FALSE)

```

### Resource rents

As the resource rents indicator from the World Bank included rents from mineral resources and forests, an indicator only including resource rents from coal, oil, and natural gas was constructed.

```{r}

# continue here

rr_oil <- read.csv(here::here("04_data_cleaning/controls/World Bank/World_Bank_Oil_Rents_GDP.csv"))%>%
  janitor::clean_names()%>%  
  subset(select = -c(i_series_name, series_code, country_code))%>%
  mutate_at(vars(-country_name), as.numeric)%>%
  pivot_longer(cols = !country_name, names_to = "year", values_to = "oil_rents")%>%
  mutate(year=substr(year,9,12))%>%
  mutate(iso = countrycode(country_name, origin = 'country.name', destination = 'iso3c'))%>%
  filter(!country_name %in% na_countries)%>%
  mutate_at(c("year", "oil_rents"), as.numeric)

rr_coal <- read.csv(here::here("04_data_cleaning/controls/World Bank/World_Bank_Coal_Rents_GDP.csv"))%>%
  janitor::clean_names()%>%  
  subset(select = -c(i_series_name, series_code, country_code))%>%
  mutate_at(vars(-country_name), as.numeric)%>%
  pivot_longer(cols = !country_name, names_to = "year", values_to = "coal_rents")%>%
  mutate(year=substr(year,9,12))%>%
  mutate(iso = countrycode(country_name, origin = 'country.name', destination = 'iso3c'))%>%
  filter(!country_name %in% na_countries)%>%
  mutate_at(c("year", "coal_rents"), as.numeric)


rr_ng <- read.csv(here::here("04_data_cleaning/controls/World Bank/World_Bank_Natural_Gas_Rents_GDP.csv"))%>%
  janitor::clean_names()%>%  
  subset(select = -c(i_series_name, series_code, country_code))%>%
  mutate_at(vars(-country_name), as.numeric)%>%
  pivot_longer(cols = !country_name, names_to = "year", values_to = "gas_rents")%>%
  mutate(year=substr(year,9,12))%>%
  mutate(iso = countrycode(country_name, origin = 'country.name', destination = 'iso3c'))%>%
  filter(!country_name %in% na_countries)%>%
  mutate_at(c("year", "gas_rents"), as.numeric)

rr <- rr_oil%>%
  full_join(rr_coal, by = c("iso", "year"))%>%
  full_join(rr_ng, by = c("iso", "year"))%>%
  subset(select = c(country_name, iso, year, oil_rents, coal_rents, gas_rents))%>%
  mutate(resource_rents = rowSums(.[4:6], na.rm = TRUE))%>%
  rename(country = country_name)%>%
  mutate(country = countrycode(country, origin = 'country.name', destination = 'country.name'))


write.csv(rr, here::here("05_clean_data/resource_rents_share_gdp.csv"), row.names = FALSE)


```



# Export model


### Resource prices

```{r}

# Average Crude Oil Prices 
oil_prices <- read_xlsx(here::here("04_data_cleaning/Controls/bp/bp-stats-review-2021-all-data.xlsx"), sheet = "Oil - Crude prices since 1861", skip = 3)%>%
  clean_names()%>%
  rename(oil_price = x2020)%>%
  transform(year = as.numeric(year))%>%
  filter(year >= 2000)%>%
  subset(select = - 2)


# Average natural gas prices
ng_prices <- read_xlsx(here::here("04_data_cleaning/Controls/bp/bp-stats-review-2021-all-data.xlsx"), sheet = "Gas - Prices ", skip = 4)%>%
  janitor::clean_names()%>%
  transform(x1 = as.numeric(x1))%>%
  filter(x1 >= 2000)%>%
  subset(select = -countries_cif_6)%>%
  rowwise() %>% 
  mutate(average_ng_price = mean(c(cif1:alberta_5)))%>%
  subset(select = c(x1, average_ng_price))%>%
  rename(year = x1)


# Average coal prices
coal_prices <- read_xlsx(here::here("04_data_cleaning/Controls/bp/bp-stats-review-2021-all-data.xlsx"), sheet = "Coal - Prices", skip = 1)%>%
  janitor::clean_names()%>%
  rename(year = us_dollars_per_tonne)%>%
  transform(year = as.numeric(year))%>%
  filter_all(any_vars(!is.na(.)))%>% #removing rows that are all na
  filter(year >= 2000)

coal_prices <- coal_prices[,colSums(is.na(coal_prices))<nrow(coal_prices)]%>% # removing all na columns
  rowwise() %>% 
  mutate(average_coal_price = mean(c(northwest_europe_marker_price:asian_marker_price)))%>%
  subset(select = c(year, average_coal_price))


fossil_prices = oil_prices%>%
  full_join(ng_prices, by = "year")%>%
  full_join(coal_prices, by = "year")

plotdf <- fossil_prices%>%
  pivot_longer(cols = !year, names_to = "fuel", values_to = "price")


ggplot(plotdf, aes(x=year, y=price)) +
  geom_line(aes(colour = as.factor(fuel)))


write.csv(fossil_prices, here::here("05_clean_data/fossil_prices.csv"), row.names = FALSE)


```

#### Infrastructural Quality


```{r}

i_q_2007 <- read_xlsx(here::here("04_data_cleaning/controls/International_LPI_from_2007_to_2018.xlsx"), sheet = "2007", skip = 2)%>%
  clean_names()%>%
  subset(select = c(country, score_3))%>%
  mutate(country = ifelse(country == "Buthan", sub("Buthan", "Bhutan", country),country))%>%
  mutate(country = countrycode(country, origin = 'country.name', destination = 'country.name'))%>%
  mutate(iso = countrycode(country, origin = 'country.name', destination = 'iso3c'))%>%
  rename(lpi_2007 = score_3)

i_q_2010 <- read_xlsx(here::here("04_data_cleaning/controls/International_LPI_from_2007_to_2018.xlsx"), sheet = "2010", skip = 2)%>%
  clean_names()%>%
  subset(select = c(country, score_3))%>%
  mutate(country = ifelse(country == "Buthan", sub("Buthan", "Bhutan", country), country))%>%
  mutate(country = countrycode(country, origin = 'country.name', destination = 'country.name'))%>%
  mutate(iso = countrycode(country, origin = 'country.name', destination = 'iso3c'))%>%
  rename(lpi_2010 = score_3)

i_q_2012 <- read_xlsx(here::here("04_data_cleaning/controls/International_LPI_from_2007_to_2018.xlsx"), sheet = "2012", skip = 2)%>%
  clean_names()%>%
  subset(select = c(country, score_3))%>%
   mutate(country = ifelse(country == "Buthan", sub("Buthan", "Bhutan", country),
                          ifelse(country == "Sco Tomi and Principe", sub("Sco Tomi and Principe", "Sao Tome and Principe", 
                                                                         country),country)))%>%
  mutate(country = countrycode(country, origin = 'country.name', destination = 'country.name'))%>%
  mutate(iso = countrycode(country, origin = 'country.name', destination = 'iso3c'))%>%
  rename(lpi_2012 = score_3)

i_q_2014 <- read_xlsx(here::here("04_data_cleaning/controls/International_LPI_from_2007_to_2018.xlsx"), sheet = "2014", skip = 2)%>%
  clean_names()%>%
  subset(select = c(country, score_3))%>%
  mutate(country = ifelse(country == "Buthan", sub("Buthan", "Bhutan", country),
                          ifelse(country == "Sco Tomi and Principe", sub("Sco Tomi and Principe", "Sao Tome and Principe", 
                                                                         country),country)))%>%
  mutate(country = countrycode(country, origin = 'country.name', destination = 'country.name'))%>%
  mutate(iso = countrycode(country, origin = 'country.name', destination = 'iso3c'))%>%
  rename(lpi_2014 = score_3)

i_q_2016 <- read_xlsx(here::here("04_data_cleaning/controls/International_LPI_from_2007_to_2018.xlsx"), sheet = "2016", skip = 2)%>%
  clean_names()%>%
  subset(select = c(country, score_3))%>%
  mutate(country = ifelse(country == "Buthan", sub("Buthan", "Bhutan", country),country))%>%
  mutate(country = countrycode(country, origin = 'country.name', destination = 'country.name'))%>%
  mutate(iso = countrycode(country, origin = 'country.name', destination = 'iso3c'))%>%
  rename(lpi_2016 = score_3)

i_q_2018 <- read_xlsx(here::here("04_data_cleaning/controls/International_LPI_from_2007_to_2018.xlsx"), sheet = "2018", skip = 2)%>%
  clean_names()%>%
  subset(select = c(country, score_3))%>%
  mutate(country = ifelse(country == "Buthan", sub("Buthan", "Bhutan", country),country))%>%
  mutate(country = countrycode(country, origin = 'country.name', destination = 'country.name'))%>%
  mutate(iso = countrycode(country, origin = 'country.name', destination = 'iso3c'))%>%
  rename(lpi_2018 = score_3)

infra_qual <- i_q_2007%>%
  full_join(i_q_2010, by = c("iso", "country"))%>%
  full_join(i_q_2012, by = c("iso", "country"))%>%
  full_join(i_q_2014, by = c("iso", "country"))%>%
  full_join(i_q_2016, by = c("iso", "country"))%>%
  full_join(i_q_2018, by = c("iso", "country"))

infra_qual <- infra_qual%>%
  rowwise() %>%
  mutate(lpi_2008 = mean(c(lpi_2007, lpi_2010), na.rm = TRUE))%>%
  mutate(lpi_2009 = mean(c(lpi_2007, lpi_2010), na.rm = T))%>%
  mutate(lpi_2011 = mean(c(lpi_2010, lpi_2012), na.rm = T))%>%
  mutate(lpi_2013 = mean(c(lpi_2012, lpi_2014), na.rm = T))%>%
  mutate(lpi_2015 = mean(c(lpi_2014, lpi_2016), na.rm = T))%>%
  mutate(lpi_2017 = mean(c(lpi_2016, lpi_2018), na.rm = T))
  
infra_qual <- infra_qual%>%
  pivot_longer(cols = !c(country, iso), names_to = "year", values_to = "lpi")%>%  
  mutate(year=substr(year,5,8))%>%
  mutate(year = as.numeric(year))%>%
  group_by(country)%>%
  arrange(country, year)

  
write.csv(infra_qual, here::here("05_clean_data/quality_of_infrastructure.csv"), row.names = FALSE)

```


### Global Shipping Connectivity
* continue here: all cols are characters, need to change that

```{r}

shipping <- read_xlsx(here::here("04_data_cleaning/controls/unctad_shipping_liner connectivity.xlsx"), skip = 4)%>%
  clean_names()%>%
  filter(quarter != "ECONOMY")%>%
  rename(country = quarter)%>%
  mutate(across(q1_2006:q4_2021, as.numeric))%>%
  subset(!country %in% c("Falkland Islands (Malvinas)", "Christmas Island"))%>%
  rowwise()%>%
  mutate(y2006 = mean(q1_2006, q2_2006,q3_2006, q4_2006, na.rm = TRUE))%>%
  mutate(y2007 = mean(q1_2007, q2_2007,q3_2007, q4_2007, na.rm = TRUE))%>%
  mutate(y2008 = mean(q1_2008, q2_2008,q3_2008, q4_2008, na.rm = TRUE))%>%
  mutate(y2009 = mean(q1_2009, q2_2009,q3_2009, q4_2009, na.rm = TRUE))%>%
  mutate(y2010 = mean(q1_2010, q2_2010,q3_2010, q4_2010, na.rm = TRUE))%>%
  mutate(y2011 = mean(q1_2011, q2_2011,q3_2011, q4_2011, na.rm = TRUE))%>%
  mutate(y2012 = mean(q1_2012, q2_2012,q3_2012, q4_2012, na.rm = TRUE))%>%
  mutate(y2013 = mean(q1_2013, q2_2013,q3_2013, q4_2013, na.rm = TRUE))%>%
  mutate(y2014 = mean(q1_2014, q2_2014,q3_2014, q4_2014, na.rm = TRUE))%>%
  mutate(y2015 = mean(q1_2015, q2_2015,q3_2015, q4_2015, na.rm = TRUE))%>%
  mutate(y2016 = mean(q1_2016, q2_2016,q3_2016, q4_2016, na.rm = TRUE))%>%
  mutate(y2017 = mean(q1_2017, q2_2017,q3_2017, q4_2017, na.rm = TRUE))%>%
  mutate(y2018 = mean(q1_2018, q2_2018,q3_2018, q4_2018, na.rm = TRUE))%>%
  mutate(y2019 = mean(q1_2019, q2_2019,q3_2019, q4_2019, na.rm = TRUE))%>%
  mutate(y2020 = mean(q1_2020, q2_2020,q3_2020, q4_2020, na.rm = TRUE))%>%
  mutate(y2010 = mean(q1_2021, q2_2021,q3_2021, q4_2021, na.rm = TRUE))%>%
  select(-contains("q"))%>%
  pivot_longer(cols = !country, names_to = "year", values_to = "connectivity_index")%>%
  mutate(year = substr(year, 2,5))%>%
  mutate(iso = countrycode(country, origin = 'country.name', destination = 'iso3c'))%>%
  mutate(country = countrycode(country, origin = 'country.name', destination = 'country.name'))


write.csv(shipping, here::here("05_clean_data/shipping_connectivity.csv"), row.names = FALSE)


```








### Electricity prices

Data on electricity prices is only available for 2015-2020 and will probably not be used as a control.
```{r electricity prices}
electricity_price <- read.csv(here::here("./Controls/World Bank/price_of_electricity_US_cents_kWh_Data.csv"), header = TRUE, sep = ",", quote = "\"", 
                 dec = ".", fill = TRUE, comment.char = "")%>%
  as.data.frame()%>%
  clean_names()
# Removing cities
electricity_price <- electricity_price[-c(1:22),]

write_csv(electricity_price, "electricity_price.csv")
```

