---
title: "Data Cleaning Energy Consumption and Trade"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Cleaning energy consumption and trade 

This script contains modifications made to the OWID dataset on energy consumption 

# OWID

```{r libraries, echo=FALSE}
library(tidyverse)
library(countrycode)
```

Composite observations, disputed and overseas territories were removed, and years limited to 2000 - 2019, as data for 2020 was not available for most countries. Lastly, countrycode was used to standardise the country names. "Timor" was renamed to "Timor-Leste" beforehand because countrycode could not identify it. 

```{r loading and cleaning data}
df_owid <- readxl::read_xlsx(here::here("04_data_cleaning/energy_consumption_data/owid-energy-data_21.xlsx"))%>%
  as.data.frame()

df_owid <- df_owid %>%
  mutate(country = str_replace(country, "Timor", "Timor-Leste"))%>%
  subset(!country %in% c("Africa", "Asia Pacific", "CIS", "Central America", "Eastern Africa", "Europe",
                         "Europe (other)", "Middle Africa", "Middle East",  "North America",
                         "Northern Mariana Islands", "OPEC", "Other CIS", "Other Asia & Pacific", 
                         "Other Caribbean", "Other Northern Africa", "Other Southern Africa", 
                         "Other Middle East", "Other South America", "South & Central America", 
                         "United States Pacific Islands", "USSR", "Western Africa", "World",
                         "Yugoslavia", "Reunion", "Saint Helena", "Western Sahara") &  year >= 2005 
                          & year < 2020)%>%
  mutate(country = countrycode(country, origin = 'country.name', destination = 'country.name'))%>%
  mutate(region = countrycode(country, origin = 'country.name', destination = 'region'))%>%
  mutate(iso = countrycode(country, origin = 'country.name', destination = 'iso3c'))


# Check which countries remain: 214 countries or independent territories
unique(df_owid$country)

```
## Choosing the best Dv measure

The dataset was then examined for the data availability of the various variables. The two variables fossil_cons_per_capita and fossil_share_energy were subsequently chosen for closer examination. Even though significantly more data points were available for fossil_cons_per_capita, a comparison of the variable to energy_per_capita showed that it cannot be an accurate measure of per-capita fossil fuel consumption, as the share it has in energy_per_capita is much too low for many countries with carbon-intensive energy mixes. For this reason, the variable fossil_share_energy, which contains less observations, but seems to be an adequate measure of the share of fossil fuels in the total energy mix, was chosen as dependent variable in the analysis.

```{r checking variables}
data_avail <- df_owid %>%
  sapply(function(x) sum(!is.na(x)))%>%
  as.data.frame()

data_avail_fossil_cons <- df_owid %>% 
  group_by(country)%>%
  tally(!is.na(fossil_cons_per_capita))%>%
  subset(n > 0)

test <- df_owid %>%
  subset(select = c(1:3, fossil_cons_per_capita, energy_per_capita))

data_avail_fossil_share <- df_owid %>% 
  group_by(country)%>%
  tally(!is.na(fossil_share_energy))%>%
  subset(n > 0)

```

The dataset was then reduced to those variables needed for the descriptive analysis and the regression analysis.

fossil_share_energy = Share of primary energy consumption that comes from fossil fuels

Observations were examined for NAs, and those that contained only NAs in fossil_share_energy were removed.


```{r reducing dataset}

# Checking for countries which contain NAs in the relevant variable
owid_test <- df_owid %>%
  filter(is.na(fossil_share_energy))%>%
  subset(select = c(1:3, fossil_share_energy))

# Checking whether all year observations (2000 - 2019) are NA per country
owid_test <- owid_test%>%
  count(country)

# Manually checking those countries for which NA < 20: Those contained fewer observations, still all observations are NA
owid_test <- owid_test%>%
  subset(n < 20)

# Removing countries with only missing values
owid_fcpc <- df_owid %>%
  filter(!is.na(fossil_share_energy))%>%
  subset(select = c(2:3, fossil_share_energy, fossil_energy_per_capita, energy_per_capita, region, iso))

#Testing for NAs in relevant variable: no NAs
test <- owid_fcpc%>%
  subset(is.na(fossil_share_energy))

write.csv(owid_fcpc, (here::here("05_clean_data/owid_data.csv")),  row.names=FALSE)
```

Lastly, the years and countries which are represented in the dependent variable data were examined. As each country has 20 associated year-observation, and the min and max values lie at 2000 and 2019, there are no missing years.

A big drawback of the limited number of states for which this data are available is the fact that no countries in Sub-Saharan Africa except South Africa are included in the dataset, which strongly reduces the informative value of the data. 

```{r missing years/countries}
#testing for missing years
test <- owid_fcpc%>%
  count(country)

min(owid_fcpc$year)
max(owid_fcpc$year)

# checking countries
unique(owid_fcpc$country)

test <- owid_fcpc%>%
  group_by(region)%>%
  summarise(count = n_distinct(country))

```

The data was transferred into panel format and will be used in analysis_1

```{r}

library(plm)
df_owid.p <- pdata.frame(df_owid, index= c("country", "year"))




```

