---
title: "Visualizations Descriptive Analysis Investments"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Visualizations for descriptive data analysis



```{r libraries, echo=FALSE}
library(tidyverse)
library(ggplot2)
library(rnaturalearth)
library(sf)
library(countrycode)
library(viridis)
library(readxl)
library(here)
library(RColorBrewer)
library(pals)
library(xtable)
library(tidyr)
library(janitor)
library(arsenal)
library(gt)
library(magrittr)
library(webshot)
library(scales)
library(paletteer)
library(plotly)
library(htmlwidgets)

theme_set(theme_bw())
options(scipen=999)

```



```{r loading data}

world <- ne_countries(scale = 'medium', returnclass = 'sf')%>%
  mutate(iso = countrycode(sovereignt, origin = 'country.name', destination = 'iso3c'))
inv <- read_csv(here::here("05_clean_data/investments_gdpshare.csv"), show_col_types = FALSE)
```

Regional distribution of investments 

```{r worldmap}
investments_quant <- inv%>%
  group_by(country)%>%
  summarise(investments = sum(investment))%>%
  mutate(iso = countrycode(country, origin = 'country.name', destination = 'iso3c'))

investments_quant_geom <- merge(world, investments_quant, by = "iso", all.x = T)%>%
  subset(sovereignt != "Antarctica")%>%
  filter(type != "Dependency")

ggplot(data = investments_quant_geom) +
  geom_sf(aes(fill = investments)) +
  scale_fill_viridis(option = "mako",
                      direction = -1,
                      na.value = "lavenderblush3",
                      breaks=seq(min(investments_quant_geom$investments, na.rm = T),
                                max(investments_quant_geom$investments, na.rm = T),
                                (max(investments_quant_geom$investments, na.rm = T)
                                 -min(investments_quant_geom$investments, na.rm = T))/4))+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        text = element_text(size=20))+
  ggtitle("Chinese overseas energy and transport investments", subtitle = "Investments from 2005 - 2020, Source: American Enterprise Institute (2021)") +
  labs(fill = "Cumulative investments in million USD")

ggsave(here("06_tables_and_plots/map_energy_and_transport_investments_usd.pdf"), width=15, height = 5, dpi = 300)

```

Tables of investment structure by sector in ten major investment destinations

```{r heatmap}
which.max(investments_quant$investments)
investments_quant[,28]

#Selecting ten major investment destinations
max_inv <- investments_quant[with(investments_quant,order(-investments)),]
max_inv <- max_inv[1:10,]%>%
  subset(select = c(country, investments))

# Calculating investments by sector
investments_share <- inv%>%
  group_by(country, subsector)%>%
  summarise(investmentshare = sum(investment))%>%
  filter(country %in% max_inv$country)
  
investments_share$subsector <- as.factor(investments_share$subsector)
investments_share <- spread(investments_share, key = subsector, value = investmentshare)%>%
  mutate(test = rowSums(across(where(is.numeric)), na.rm=T))

investments_share <- investments_share[with(investments_share,order(-test)),]%>%
  subset(select = -test)%>%
  adorn_totals("row")

investments_share_percent <- investments_share%>%
  rename(
    Country = country,
    Unknown = '<NA>'
  )%>%
  ungroup() %>%
  mutate(across(where(is.numeric))/rowSums(across(where(is.numeric)), na.rm = T))%>%
  mutate_at(vars(-Country), funs(round(., 2)))
  
col_order <- c("Country" ,"Coal", "Oil", "Gas", "Hydro", "Alternative",
               "Rail", "Shipping", "Unknown" )
investments_share_percent <- investments_share_percent[, col_order]

# plain table
print(xtable(investments_share_percent), file = "sector_percentages_by_country")


# Heatmap table ----

full_val_range <- investments_share_percent %>% 
  drop_na()%>%
  ungroup %>%
  select_if(is.numeric) %>% 
  range

tab1 <- investments_share_percent%>%
  replace(is.na(.), 0)%>%
  gt() %>%
  tab_header(
    title = "Investment shares to subsectors by country",
    subtitle = "The top ten investment destinations, sorted by total investment volume, are presented"
  )%>%
  data_color(
    columns = c(Alternative, Hydro, Gas, Oil, Coal, Rail, Shipping, Unknown),
    colors = scales::col_numeric(
      palette = rev(as.character(paletteer::paletteer_c('viridis::mako', 150))),
      domain = full_val_range))%>%
  tab_options(
      table_body.hlines.width = 3.5)%>%
  tab_source_note(
    source_note = md("Source: American Enterprise Institute (2021). *China Global Investment Tracker*.")
  )

gtsave(tab1, "./06_tables_and_plots/heattable_investments_shares.png") #run this from console

```


Testing how many investments took place within the BRI compared to outside of it.

```{r get overview over bri data}
test <- inv %>%
  count(bri)%>%
  mutate(share = n/sum(n))

test <- inv%>%
  filter(bri == 1)%>%
  count(year_investment)%>%
  mutate(share = n/sum(n))

sum(test$share[which(test$year_investment >=2018)])

# Calculating investments by BRI
test <- inv%>%
  group_by(bri)%>%
  summarise(investmentshare = sum(investment))%>%
  mutate(share = investmentshare/sum(investmentshare))


```

Sectoral distribution of investments worldwide

```{r}
my_palette <- brewer.pal(name="BrBG",n=11)[c(10,9,2:4,7:8)]
my.labels <- c("East Asia &\nPacific",
               "Europe &\nCentral Asia", 
               "Latin America &\nCaribbean",
               "Middle East &\nNorth Africa",
               "North\nAmerica",
               "South\nAsia",
               "Sub-Saharan\nAfrica")
#labels = c("Alternative", "Coal", "Oil", "Gas", "Hydro", "Rail", "Shipping", "NA")

#By activating geom_text, percentage labels can be added. Did not do this because the graph became too crowded
plot_df <- inv%>%
  group_by(region) %>%
  count(region, subsector)%>%    
         mutate(pct=n/sum(n),               
                ypos = cumsum(n) - 0.5*n)

ggplot(data = plot_df, aes(fill = factor(subsector, levels=c("Alternative", "Hydro", "Coal", "Oil", "Gas", "Rail", "Shipping", NA)), x = region, y = n))+
  geom_bar(position="stack", stat="identity")+
  scale_fill_manual(values = my_palette, labels = c("Alternative", "Hydro", "Coal", "Oil", "Gas", "Rail", "Shipping", "NA")) +
  #geom_text(aes(label = round(pct, 2)), colour = "white", position=position_stack(vjust=0.5))+
  theme(
    legend.text=element_text(size=rel(1.5))
  )+
  theme_bw() +
  mdthemes::md_theme_classic() +
  ggtitle("Investments by subsector and world region", subtitle = "Source: American Enterprise Institute (2021). *China Global Investment Tracker*.")+
  labs(x = "World region", y = "Investments in million USD", fill = "Subsector")+
  scale_x_discrete(guide = guide_axis(n.dodge=3))


ggsave(here("06_tables_and_plots/investment_share_subsectors.png"), width = 7, height = 7, dpi = 300)
  

```


```{r}

test <- inv%>%
  group_by(region, subsector, bri)%>%
  summarise(investmentshare = sum(investment))
  
test$subsector <- as.factor(test$subsector)
test <- spread(test, key = subsector, value = investmentshare)%>%
  mutate(sum = rowSums(across(where(is.numeric)), na.rm=T))

test <- test[with(test,order(-sum)),]%>%
  subset(select = -sum)%>%
  adorn_totals("row")

total_investments_share_percent <- test%>%
  rename(
    Region = region,
    Unknown = '<NA>'
  )%>%
  ungroup() %>%
  mutate(across(Alternative:Unknown)/rowSums(across(Alternative:Unknown), na.rm = T))%>%
  mutate_at(vars(Alternative:Unknown), funs(round(., 2)))

total_investments_share_percent <- total_investments_share_percent%>%
  mutate(fossil_sum = rowSums(select(.,c(Coal, Gas, Oil)), na.rm=T))%>%
  mutate(lc_sum = rowSums(select(.,c(Alternative, Hydro)), na.rm=T))%>%
  mutate(transport_sum = rowSums(select(.,c(Rail, Shipping)), na.rm=T))%>%
  arrange(Region)



```


Checking and plotting OFDI flows for context chapter:

```{r}
test <- inv%>%
  group_by(year_investment)%>%
  summarize(inv_sum = sum(investment))

test %>%
  filter(year_investment %in% c(2012:2014))%>%
  summarize(inv_sum2 = sum(inv_sum))

test %>%
  filter(year_investment %in% c(2015:2017))%>%
  summarize(inv_sum3 = sum(inv_sum))



g <- ggplot(data = test, aes(x = year_investment, y = inv_sum)) +
  geom_line()
g1 <- ggplotly(g)
saveWidget(g1, here("06_tables_and_plots/ofdis.html"))
```


## Comparing sectoral shares between BRI and general investments

### To Do:
* examine countries between nonBRI and BRI

```{r}

# Summing rowwise: Which share of overall investments in Alternatives, FF, etc. took place in the BRI compared to before the BRI

bri_shares_by_subsector <- inv%>%
  group_by(subsector) %>%
  summarize(sumnonBRI = sum(investment[bri == 0]),
            sumBRI = sum(investment[bri==1]))%>%
  mutate(sum = rowSums(.[2:3]))%>%
  mutate(sumnonBRI = sumnonBRI/sum,
         sumBRI = sumBRI/sum)


# Summing colwise: Which share of overall investments in the BRI/ before it went into alternatives/ fossil fuels?

sectoral_shares_by_bri <- inv%>%
  group_by(subsector) %>%
  summarize(sumnonBRI = sum(investment[bri == 0]),
            sumBRI = sum(investment[bri==1]))%>%
  mutate_at(vars(c(sumnonBRI, sumBRI)),  funs(./sum(.)))

```

Ergebnis: Verhältnis fossile:erneuerbare Energien deutlich grüner in BRI, trotzdem korrelieren BRI Investitionen mit höherem Konsum fossiler Energien. Warum??


## Descriptive Tables for Data chapter 


```{r}
ivstock_exp <- read_csv(here::here("05_clean_data/df_investmentstock_all_exports.csv"), show_col_types = FALSE)
ivstock_fs <- read_csv(here::here("05_clean_data/df_continuous_all_consumption.csv"), show_col_types = FALSE)

length(unique(ivstock_fs$country))
length(unique(ivstock_exp$country))

test <- ivstock_fs%>%
  distinct(country, .keep_all = TRUE)%>%
  count(region)

test2 <- ivstock_exp%>%
  distinct(country, .keep_all = TRUE)%>%
  count(region)

testmerge <- full_join(test, test2, by = "region")%>%
  rename(consumption.df = n.x,
         exports.df = n.y)


stargazer(testmerge, summary = FALSE, rownames = FALSE,
          column.labels = c("World region", "Countries in consumption dataframe", "Countries in export dataframe"),
           add.lines = list(c("Sum", "69", "146")))


```




