---
title: "analysis_2"
author: "Sarah Wenzel"
date: "16 2 2022"
output: 
  pdf_document: 
    keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this script, a panel regression will be estimated to examine the effect of Chinese investments on the share of fossil fuels used in a country's energy mix. 

```{r libraries, message=FALSE}
library(tidyverse)
library(AER)
library(plm)
library(stargazer)
library(texreg)
library(ggpubr)
library(lmtest) #for bptest
library(lme4)
library(funtimes) # for trend testing
options(scipen=999)
```



```{r loading data}
ivstock_fs <- read_csv(here::here("05_clean_data/df_continuous_all_consumption.csv"), show_col_types = FALSE)%>%
  mutate(region = as.factor(region),
         region = relevel(region, ref = "North America"))
ffivstock_fs <- read_csv(here::here("05_clean_data/df_ffcontinuous_consumption.csv"), show_col_types = FALSE)
lcivstock_fs <- read_csv(here::here("05_clean_data/df_lccontinuous_consumption.csv"), show_col_types = FALSE)
trivstock_fs <- read_csv(here::here("05_clean_data/df_transportcontinuous_consumption.csv"), show_col_types = FALSE)

```




# Checking for multicollinearity, normality, heteroskedasticity, and serial correlation

```{r}
# Testing for multicollinearity, correlation should not be > 0.7
reg_data <- ffivstock_fs[, c(7:16)]%>%
  na.omit()
test <- cor(reg_data)
test

# testing for normality, p-value should be > 0.05
shapiro.test((ffivstock_fs$fossil_share_energy))

plot(fossil_share_energy ~ gdp, data=ffivstock_fs)
plot(fossil_share_energy ~ resource_rents, data=ffivstock_fs)
plot(fs_mod5)

# testing for heteroskedasticity, p-value should be > 0.05
bptest(fossil_share_energy ~ gdp + pop_size +  inv_dummy +  bri_dummy + industry_share +  resource_rents + urban_pop_share + trade_share_gdp +  country + year, data = binary_fs )

# Wooldridge's test for serial correlation
pwartest(fs_ivstock)

# Pesaran’s CD test for cross-sectional dependence
pcdtest(fs_ivstock)

```

Result: Most predictors are not strongly correlated. However, the share of industry in a country's GDP is strongly correlated with the share of resource rents in a country's GDP. Only one of these variables should be included in a model at a given time.

The dependent variable not normally distributed, which should be okay due to the large sample size. 
The data is characterized by both by heteroskedasticity, serial and cross-sectional correlation, which is why robust standard errors are used in the estimation.


## To Do:

* Collischon & Eberl 2020 fertiglesen




## Testing investment stock var (as GDP share) for trend

```{r}

ggplot(cont_iv_stock_fs, aes(y = investment_stock, x = year)) +
  geom_jitter()


notrend_test(ivstock_fs$investment_stock)
notrend_test(ivstock_fs$bri_investment_stock)

  
ggplot(test, aes(y = investment_stock, x = year)) +
  geom_jitter()

```

The plot shows that there is a trend in the investment stock data. For this reason, a trend control is introduced in the subsequent analysis.

## Investment stock (all investments)

```{r}

# Country and year FE, all investments
# year effects remove trend dummy, country effects remove regions
fs_ivstock <- plm(fossil_share_energy ~  investment_stock + gdp + trade_share_gdp +  resource_rents + urban_pop_share + pop_size + country + year + time + investment_stock*resource_rents,
               data = ivstock_fs,
               index = c("country", "year"), 
               model = "within",
               effect = "twoways")
coeftest(fs_ivstock, vcov. = vcovSCC, type = "HC0") 
cov_fs_ivstock <- vcovSCC(fs_ivstock, type = "HC0")
robust_se_fsivstock <- sqrt(diag(cov_fs_ivstock))


fs_ivstock_yfe <- plm(fossil_share_energy ~ investment_stock + gdp + trade_share_gdp +  resource_rents + urban_pop_share + pop_size +   investment_stock*resource_rents + investment_stock*region + year,
               data = ivstock_fs,
               index = c("country", "year"), 
               model = "within",
               effect = "time")
coeftest(fs_ivstock_yfe, vcov. = vcovSCC, type = "HC0")
cov_fs_ivstock_yfe <- vcovSCC(fs_ivstock_yfe, type = "HC0")
robust_se_fsivstockyfe <- sqrt(diag(cov_fs_ivstock_yfe))


fs_ivstock_cfe <- plm(fossil_share_energy ~ investment_stock + gdp + trade_share_gdp +  resource_rents + urban_pop_share + pop_size + investment_stock*resource_rents + country + time,
               data = ivstock_fs,
               index = c("country", "year"), 
               model = "within",
               effect = "individual")
coeftest(fs_ivstock_cfe, vcov. = vcovSCC, type = "HC0")
cov_fs_ivstock_cfe <- vcovSCC(fs_ivstock_cfe, type = "HC0")
robust_se_fsivstockcfe <- sqrt(diag(cov_fs_ivstock_cfe))


# Random effects model

fs_ivstock_re <- plm(fossil_share_energy ~  investment_stock + gdp + trade_share_gdp +  resource_rents + urban_pop_share + pop_size + industry_share + country + year + time + investment_stock*bri_dummy,
               data = ivstock_fs,
               index = c("country", "year"), 
               model = "random",
               random.method = "nerlove")
coeftest(fs_ivstock, vcov. = vcovSCC, type = "HC0") 
cov_fs_ivstock <- vcovSCC(fs_ivstock, type = "HC0")
robust_se2 <- sqrt(diag(cov_fs_ivstock))

```


## Note: Variance-covariance matrices

*vcovSCC: Driscoll and Kraay (1998) Robust Covariance Matrix Estimator: robust covariance matrix of parameters for a panel model, which is consistent with cross--sectional and serial correlation, developed specifically for macro datasets characterized by spatial dependence
vcovNW: Newey and West(1987) Robust Covariance Matrix Estimator: restriction of the Driscoll and Kraay (1998) covariance to no cross-sectional correlation


vcovHC: White’s heteroskedasticity-consistent covariance matrix: consistent against serial correlation, but not cross-sectional correlation (https://cran.r-project.org/web/packages/plm/vignettes/A_plmPackage.html)
vcovBK: Beck and Katz Robust Covariance Matrix Estimators: controls either for serial or for cross-sectional correlation
! vcovDC: Double-Clustering Robust Covariance Matrix Estimator, errors clustering along both dimensions. Summing a group- and a time-clustered covariance matrix and subtracting a diagonal one a la White


## Hausmann test

```{r}

phtest(fs_ivstock, fs_ivstock_re)

```

Result: The random effects model is biased, fixed effects will be used.



## Disaggregated Investment Stock Variables

All disaggregated investment stock variables were estimated using country fixed effects and a time variable to control for the trend in the independent variable.



```{r}

# Fossil fuel investment stock, country effects and trend control
fs_ffivstock <- plm(fossil_share_energy ~ investment_stock + gdp + trade_share_gdp + urban_pop_share + pop_size +  investment_stock*resource_rents + country + time,
               data = ffivstock_fs,
               index = c("country", "year"), 
               model = "within",
               effect = "individual")
coeftest(fs_ffivstock, vcov. = vcovSCC, type = "HC0")
cov_fs_ffivstock <- vcovSCC(fs_ffivstock, type = "HC0")
robust_se_ff <- sqrt(diag(cov_fs_ffivstock))

# Low carbon investment stock, country FE, trend control
fs_lcivstock <- plm(fossil_share_energy ~ investment_stock + gdp + trade_share_gdp + urban_pop_share + pop_size +  investment_stock*resource_rents + country + time,
               data = lcivstock_fs,
               index = c("country", "year"), 
               model = "within",
               effect = "individual")
coeftest(fs_lcivstock, vcov. = vcovSCC, type = "HC0")
cov_fs_lcivstock <- vcovSCC(fs_lcivstock, type = "HC0")
robust_se_lc <- sqrt(diag(cov_fs_lcivstock))

# Transport investment stock, country FE, trend control
fs_trivstock <- plm(fossil_share_energy ~  investment_stock + gdp + trade_share_gdp + urban_pop_share + pop_size + investment_stock*resource_rents +  country + time,
               data = trivstock_fs,
               index = c("country", "year"), 
               model = "within",
               effect = "individual")
coeftest(fs_trivstock, vcov. = vcovSCC, type = "HC0") 
cov_fs_trivstock <- vcovSCC(fs_trivstock, type = "HC0")
robust_se_tr <- sqrt(diag(cov_fs_trivstock))


```



## BRI investment stock

```{r}

# country fixed effects
fs_bristock <-  plm(fossil_share_energy ~ bri_investment_stock + gdp + trade_share_gdp + urban_pop_share + pop_size +  bri_investment_stock*resource_rents +  time + country,
               data = ivstock_fs,
               index = c("country", "year"), 
               model = "within",
               effect = "individual")
coeftest(fs_bristock, vcov. = vcovSCC, type = "HC0")
cov_bristock <- vcovSCC(fs_bristock, type = "HC0")
robust_se_bri <- sqrt(diag(cov_bristock))


fs_ffbristock <-  plm(fossil_share_energy ~ bri_investment_stock + gdp + trade_share_gdp + urban_pop_share + pop_size +  bri_investment_stock*resource_rents +  time + country,
               data = ffivstock_fs,
               index = c("country", "year"), 
               model = "within",
               effect = "individual")
coeftest(fs_ffbristock, vcov. = vcovSCC, type = "HC0")
cov_ffbristock <- vcovSCC(fs_ffbristock, type = "HC0")
robust_se_briff <- sqrt(diag(cov_ffbristock))

fs_lcbristock <-  plm(fossil_share_energy ~ bri_investment_stock + gdp + trade_share_gdp + urban_pop_share + pop_size +  bri_investment_stock*resource_rents +  time + country,
               data = lcivstock_fs,
               index = c("country", "year"), 
               model = "within",
               effect = "individual")
coeftest(fs_lcbristock, vcov. = vcovSCC, type = "HC0")
cov_lcbristock <- vcovSCC(fs_lcbristock, type = "HC0")
robust_se_brilc <- sqrt(diag(cov_lcbristock))



fs_trbristock <-  plm(fossil_share_energy ~ bri_investment_stock + gdp + trade_share_gdp + urban_pop_share + pop_size +  bri_investment_stock*resource_rents +  time + country,
               data = trivstock_fs,
               index = c("country", "year"), 
               model = "within",
               effect = "individual")
coeftest(fs_trbristock, vcov. = vcovSCC, type = "HC0")
cov_trbristock <- vcovSCC(fs_trbristock, type = "HC0")
robust_se_britr <- sqrt(diag(cov_trbristock))

```


## Regression outputs 

First table : Aggregated investment stock, one- and twoway fixed effects
```{r}

# Akaike calculation

Sum1 <- summary(fs_ivstock)
RSS1 <- sum(Sum1$residuals^2)
K1 <- max(fs_ivstock$assign)
N1 <- length(fs_ivstock$residuals)
n1 <- N1 - K1 - fs_ivstock$df.residual

AIC_fs_ivstock = log(RSS1/n1) + (2*K1)/n1


Sum2 <- summary(fs_ivstock_yfe)
RSS2 <- sum(Sum2$residuals^2)
K2 <- max(fs_ivstock_yfe$assign)
N2 <- length(fs_ivstock_yfe$residuals)
n2 <- N2 - K2 - fs_ivstock_yfe$df.residual

AIC_fs_ivstock_yfe = log(RSS2/n2) + (2*K2)/n2

Sum3 <- summary(fs_ivstock_cfe)
RSS3 <- sum(Sum3$residuals^2)
K3 <- max(fs_ivstock_cfe$assign)
N3 <- length(fs_ivstock_cfe$residuals)
n3 <- N3 - K3 - fs_ivstock_cfe$df.residual

AIC_fs_ivstock_cfe = log(RSS3/n3) + (2*K3)/n3

fs_ivstock$AIC <- AIC_fs_ivstock
fs_ivstock_yfe$AIC <- AIC_fs_ivstock_yfe
fs_ivstock_cfe$AIC <- AIC_fs_ivstock_cfe


stargazer(fs_ivstock, fs_ivstock_yfe, fs_ivstock_cfe,
          title = "Energy consumption and Chinese OFDI",
          dep.var.caption="Dependent variable: Fossil fuels as share of primary energy consumption",
         column.labels = c("Country and year FE", "Year FE and region controls", "Country FE and trend control"),
         dep.var.labels.include = FALSE,
         column.sep.width = "0.5pt", 
         se = list(robust_se_fsivstock, robust_se_fsivstockyfe, robust_se_fsivstockcfe), 
         single.row = TRUE,
         order = c(1:4, 14, 5:7, 15, 8, 16, 9, 17, 10, 18, 11, 19, 12, 20, 13),
         covariate.labels=c("OFDI stock", "GDP", "Trade openness", "Resource Rents", "OFDI stock*Resource Rents", "Urban population", "Log Population size", "East Asia and Pacific", "OFDI stock*East Asia and Pacific", "Europe/Central Asia", "OFDI stock*Europe/Central Asia", "Latin America and Caribbean", "OFDI stock*Latin America and Caribbean", "MENA", "OFDI stock*MENA", "South Asia", "OFDI stock*South Asia", "Sub-Saharan Africa", "OFDI stock*Sub-Saharan Africa", "Trend control"),
         keep.stat=c("aic", "adj.rsq", "n"),
          float.env = "sidewaystable")


```


Second table: Investment stock disaggregated by sectors, country fixed effects
```{r}
# Akaike calculation

Sum4 <- summary(fs_ffivstock)
RSS4 <- sum(Sum4$residuals^2)
K4 <- max(fs_ffivstock$assign)
N4 <- length(fs_ffivstock$residuals)
n4 <- N4 - K4 - fs_ffivstock$df.residual

AIC_fs_ffivstock = log(RSS4/n4) + (2*K4)/n4


Sum5 <- summary(fs_lcivstock)
RSS5 <- sum(Sum5$residuals^2)
K5 <- max(fs_lcivstock$assign)
N5 <- length(fs_lcivstock$residuals)
n5 <- N5 - K5 - fs_lcivstock$df.residual

AIC_fs_lcivstock = log(RSS5/n5) + (2*K5)/n5


Sum6 <- summary(fs_trivstock)
RSS6 <- sum(Sum6$residuals^2)
K6 <- max(fs_trivstock$assign)
N6 <- length(fs_trivstock$residuals)
n6 <- N6 - K6 - fs_trivstock$df.residual

AIC_fs_trivstock = log(RSS6/n6) + (2*K6)/n6


fs_trivstock$AIC <- AIC_fs_trivstock
fs_ffivstock$AIC <- AIC_fs_ffivstock
fs_lcivstock$AIC <- AIC_fs_lcivstock

stargazer(fs_ffivstock, fs_lcivstock, fs_trivstock,
          title = "Energy consumption and Chinese OFDI, sectoral disaggregation",
          dep.var.caption="Dependent variable: Fossil fuels as share of primary energy consumption",
         column.labels = c("Fossil fuel investment stock", "Low carbon investment stock", "Transport investment stock"),
         dep.var.labels.include = FALSE,
         column.sep.width = "6pt", 
         se = list(robust_se_ff, robust_se_lc, robust_se_tr), 
         single.row = TRUE,
         order = c(1:3, 6, 8, 4, 5, 7),
         covariate.labels=c("OFDI stock", "GDP", "Trade openness", "Resource Rents", "OFDI stock*Resource Rents", "Urban population", "Log Population size", "Trend control"),
         keep.stat=c("aic", "adj.rsq", "n"),
          float.env = "sidewaystable")

```


Third table: BRI investments, aggregated and disaggregated, country fixed effects
```{r}

# Akaike calculation

Sum7 <- summary(fs_bristock)
RSS7 <- sum(Sum7$residuals^2)
K7 <- max(fs_bristock$assign)
N7 <- length(fs_bristock$residuals)
n7 <- N7 - K7 - fs_bristock$df.residual

AIC_fs_bristock = log(RSS7/n7) + (2*K7)/n7


Sum8 <- summary(fs_ffbristock)
RSS8 <- sum(Sum8$residuals^2)
K8 <- max(fs_ffbristock$assign)
N8 <- length(fs_ffbristock$residuals)
n8 <- N8 - K8 - fs_ffbristock$df.residual

AIC_fs_ffbristock = log(RSS8/n8) + (2*K8)/n8


Sum9 <- summary(fs_lcbristock)
RSS9 <- sum(Sum9$residuals^2)
K9 <- max(fs_lcbristock$assign)
N9 <- length(fs_lcbristock$residuals)
n9 <- N9 - K9 - fs_lcbristock$df.residual

AIC_fs_lcbristock = log(RSS9/n9) + (2*K9)/n9


Sum10 <- summary(fs_trbristock)
RSS10 <- sum(Sum10$residuals^2)
K10 <- max(fs_trbristock$assign)
N10 <- length(fs_trbristock$residuals)
n10 <- N10 - K10 - fs_trbristock$df.residual

AIC_fs_trbristock = log(RSS10/n10) + (2*K10)/n10

fs_bristock$AIC <- AIC_fs_bristock
fs_ffbristock$AIC <- AIC_fs_ffbristock
fs_lcbristock$AIC <- AIC_fs_lcbristock
fs_trbristock$AIC <- AIC_fs_trbristock

stargazer(fs_bristock, fs_ffbristock, fs_lcbristock, fs_trbristock,
          title = "Energy consumption and BRI OFDI, aggregate and sectoral disaggregation",
          dep.var.caption="Dependent variable: Fossil fuels as share of primary energy consumption",
         column.labels = c("BRI investment stock", "BRI fossil fuel investment stock", "BRI low carbon investment stock", "BRI transport investment stock"),
         dep.var.labels.include = FALSE,
         column.sep.width = "6pt", 
         se = list(robust_se_bri, robust_se_briff, robust_se_brilc, robust_se_britr), 
         single.row = TRUE,
         order = c(1:3, 6, 8, 4, 5, 7),
         #covariate.labels=c("BRI OFDI stock", "GDP", "Trade openness", "Resource Rents", "OFDI stock*Resource Rents", "Urban population", "Log Population size", "Trend control"),
         keep.stat=c("aic", "adj.rsq", "n"),
          float.env = "sidewaystable")


```



## Interpretation of the regression results


In the consumption model, resource rents were shown to be negatively correlated with fossil fuel consumption. The reasons for this counterintuitive result are examined here:
```{r}
test <- ivstock_fs%>%
  group_by(country)%>%
  summarize(mean_rr = mean(resource_rents))

test <- test[with(test,order(-mean_rr)),]
median(test$mean_rr)
var(test$mean_rr)


test3 <- ivstock_fs%>%
  group_by(country)%>%
  summarize(mean_fs = mean(fossil_share_energy))

test3 <- test3[with(test3,order(-mean_fs)),]

test4 <- test3[1:10,]

```
In the BRI analysis, the low-carbon BRI IV was the only disaggregated investment variable that was positively associated with fossil fuel consumption. The reasons for this will be examined here.
```{r}

blub <- lcivstock_fs%>%
  group_by(country)%>%
  summarise(brisum = sum(bri_investment_stock))
blub <- blub[with(blub,order(-brisum)),]

```






## Information on dataset for data chapter


```{r}





```


